
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 14 - Extra: Networks of Words"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment14_extra.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, cache = TRUE)
```

-------

Following [this document](https://www.tidytextmining.com/nasa) to plot a network of words for one of the text datasets.

```{r}
library(jsonlite)

metadata <- fromJSON("https://data.nasa.gov/data.json")
names(metadata$dataset)

class(metadata$dataset$title)
#> [1] "character"
class(metadata$dataset$description)
#> [1] "character"
class(metadata$dataset$keyword)
#> [1] "list"

library(dplyr)

nasa_title <- tibble(id = metadata$dataset$`_id`$`$oid`, 
                     title = metadata$dataset$title)
nasa_title

nasa_desc <- tibble(id = metadata$dataset$`_id`$`$oid`, 
                    desc = metadata$dataset$description)
nasa_desc %>% 
  select(desc) %>% 
  sample_n(5)

library(tidyr)

nasa_keyword <- tibble(id = metadata$dataset$`_id`$`$oid`, 
                       keyword = metadata$dataset$keyword) %>%
  unnest(keyword)

nasa_keyword

my_stopwords <- tibble(word = c(as.character(1:10), 
                                "v1", "v03", "l2", "l3", "l4", "v5.2.0", 
                                "v003", "v004", "v005", "v006", "v7"))
nasa_title <- nasa_title %>% 
  anti_join(my_stopwords)
nasa_desc <- nasa_desc %>% 
  anti_join(my_stopwords)

#Most common keywords
nasa_keyword %>% 
  group_by(keyword) %>% 
  count(sort = TRUE)

nasa_keyword <- nasa_keyword %>% 
  mutate(keyword = toupper(keyword))

library(widyr)

title_word_pairs <- nasa_title %>% 
  pairwise_count(word, id, sort = TRUE, upper = FALSE)

title_word_pairs



```

