
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 7 - Extra Credits: Practice dplyr and ggplot2"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment7_extra_credits.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas



```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```


-------

1. Import the data at https://bryantstats.github.io/math421/data/ds_salaries.csv

    The data description can be found at https://www.kaggle.com/datasets/saurabhshahane/data-science-jobs-salaries

```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)

df <- read_csv("https://bryantstats.github.io/math421/data/ds_salaries.csv")
```

2. Is there any column that contains NAs?

```{r}
colSums(is.na(df))
#No NAs
```

3. What is the most frequent job title in the data?  

```{r}
df %>% count(job_title) %>% 
  arrange(-n)
#Data Scientist
```

4. Find the average salary data of the three most frequent job titles in the data. 

```{r}
#3 most frequent: Data scientist, Data engineer, data analyst
df %>% 
  filter(job_title=="Data Scientist"|job_title=="Data Engineer"|job_title=="Data Analyst") %>% 
  group_by(job_title) %>% 
  summarise(ave_sal = mean(salary))
```

5. What is the job title that have the highest average salary?

```{r}
df %>% 
  group_by(job_title) %>% 
  summarise(ave_sal = mean(salary)) %>% 
  arrange(-ave_sal)
#Head of Machine Learning
```

6. Which country gives the highest salary on average? 

```{r}
df %>% 
  group_by(company_location) %>% 
  summarise(max_sal = max(salary)) %>% 
  arrange(-max_sal)
#Country: CL
```

7. Plot five meaningful plots. All plots should have title, caption, and appropriate labels.

```{r}
#1
df %>% 
  ggplot()+
  geom_point(mapping = aes(x=work_year, y=salary, color=company_size))

#2
df %>% 
  ggplot()+
  geom_smooth(mapping = aes(x= salary, y=salary_in_usd, color=company_size))

#3
df %>% 
  ggplot()+
  geom_bar(mapping = aes(x=experience_level, fill=employment_type))

#4
df %>% 
  ggplot()+
  geom_density(mapping = aes(salary))

#5
df %>% 
  ggplot()+
  geom_histogram(mapping = aes(x=salary_in_usd))
```

