
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 8: Visualization - Making a bar race"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment8.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Install two packages `gganimate` and `gifski` then restart Rstudio. Using the `Adult Census Income` data, make an animation using `geom_point` and `transition_states`.

```{r}
# install.packages("gganimate")
# install.packages("gifski")
library(gganimate)
library(gifski)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(knitr)

df <- read_csv("~/Statistical Analysis with R/adult_census.csv")

df %>% 
  ggplot(aes(x=age, y=hours.per.week, color=sex))+
  geom_point()+
  transition_states(race)+
  labs(title = 'Race: {closest_state}')
```

2. Using the `Adult Census Income` data, make an animation using `geom_bar` and `transition_states`.

```{r}
df %>% 
  ggplot(aes(x=marital.status, fill=sex))+
  geom_bar(position = 'fill')+
  transition_states(race)+
  labs(title = 'Race: {closest_state}')
```

3. Use the WHO's dataset at [this link](https://covid19.who.int/WHO-COVID-19-global-data.csv). Make a top-10 bar race by months between countries on the number of deaths by Covid 19 in 2021.

```{r}
df <- read_csv("~/Statistical Analysis with R/WHO-COVID-19-global-data.csv") 
df <- mutate(df, Year = year(df$Date_reported),
         Months = months(df$Date_reported))

df$week <- week(df$Date_reported)
d1 <- df %>% group_by(week, Country) %>% summarise(mean = mean(New_cases))
d2 <- d1 %>% group_by(week) %>% mutate(rank=rank(-mean)) 
d3 <- d2 %>% filter(rank <= 10)
a1 <- d3 %>% ggplot(aes(x=rank, y=mean, group=Country, fill=Country, label=Country)) + geom_col()+geom_text(aes(y = mean, label = Country), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+
    labs(title = 'Week {closest_state}', x='', y='Total Number of Positive Cases', fill='Country')+
    theme(plot.title = element_text(hjust = 1, size = 22),
          axis.ticks.y = element_blank(),
          axis.text.y  = element_blank()) + 
    transition_states(week)+
    ease_aes("cubic-in-out")
animate(a1, nframes = 400)
```

4. Make a bar race using a dataset of your own interest. You may use the dataset that we use in class (https://covidtracking.com/data/download/all-states-history.csv) but you should make a different bar racev from ones in the slides. 

```{r}
df <- read_csv("~/Statistical Analysis with R/titanic.csv")

d1 <- df %>% 
  group_by(Pclass, Embarked) %>% 
  summarize(mean = mean(Fare))
d2 <- d1 %>% 
  group_by(Pclass) %>% 
  mutate(rank = rank(-mean))
d3 <- d2 %>% 
  filter(rank <= 10)

a1 <- d3 %>% 
  ggplot(aes(x=rank, y=mean, group=Embarked, label=Pclass))+
  geom_col()+
  geom_text(aes(y=mean, label=Embarked), hjust = 1.4)+
  coord_flip(clip = "off", expand = FALSE)+
  scale_x_reverse()+
  labs(title = "Pclass: {closest_state}", x='', y='Total Fare', fill = 'state')+
  theme(plot.title = element_text(hjust = 1, size = 22), axis.ticks.y = element_blank(), axis.text.y = element_blank())+
  transition_states(Pclass)+
  ease_aes("cubic-in-out")

animate(a1, nframes = 400)
```

