
---
output: # rmarkdown::github_document
  html_document:
    theme: cerulean
    toc: true
  pdf_document: default
  word_document: default
title: "Assignment 5: Handle Missing Values"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment5.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

**The data:** 

This assignment works with the Adult Census Data that can be downloaded at [this link.](https://bryantstats.github.io/math421/data/adult_census_missing.csv)

-------

**Questions**

1. Use `read_csv` to import the data.  Show the number of NAs for each columns.   

```{r}
library(tidyverse)
library(dplyr)
df <- read_csv("https://bryantstats.github.io/math421/data/adult_census_missing.csv")

colSums(is.na(df))
```

2. Using function `aggr` the VIM package to plot the number of NAs for each column. 

```{r}
#install.packages("VIM")
library("VIM")

aggr(df)
```

3. Find other forms of missing values. Hint: You can use the `table` function to check if there are suspicious categories (Unknown, for example) in a variable. What all other forms of missing values shown in the data. 

```{r}
table(df$occupation)
table(df$education)

colSums(df=="Unknown"|
          df=="Not Known"|
          df=="?", na.rm = TRUE)
```

4. Replace all the forms of missing values found to NA

```{r}
df <- df %>% 
  replace(df == "Unknown"|
          df == "Not Known"|
          df == "?", NA)
```

5. Replot the number of NAs for each column. 

```{r}
aggr(df)
```

6. Approach 1 to handle NAs: remove all rows that have any NAs. Save the dataset after removing as a different data. The original data is unchanged (still have NAs).  How many rows left after removing?

```{r}
df2 <- drop_na(df)
str(df)
#Orig. df is 32,561 rows
str(df2)
#df2 is 29,865 rows
```

7. Approach 2 to handle NAs:  Fill all the NAs with the previous or next value. (Hint: Using `fill` function).  Save the dataset after filling as a different data. The original data is unchanged (still have NAs). 

```{r}
colSums(is.na(df))

df2 <- df %>% fill(age, workclass, education, marital.status, occupation, relationship, sex, capital.gain, native.country, .direction = 'updown')

head(df2)
```

8. Approach 3 to handle NAs: For numeric variable, replace the NAs by the median.  For categorical variables, replace the NAs to the majority. 

```{r}
str(df)

median_age <- median(df$age, na.rm = TRUE)
df$age <- replace_na(df$age, median_age)

majority_workclass <- names(which.max(table(df$workclass)))
df$workclass <- replace_na(df$workclass, majority_workclass)

majority_education <- names(which.max(table(df$education)))
df$education <- replace_na(df$education, majority_education)

majority_marStatus <- names(which.max(table(df$marital.status)))
df$marital.status <- replace_na(df$marital.status, majority_marStatus)

majority_occupation <- names(which.max(table(df$occupation)))
df$occupation <- replace_na(df$occupation, majority_occupation)

majority_relationship <- names(which.max(table(df$relationship)))
df$relationship <- replace_na(df$relationship, majority_relationship)

majority_sex <- names(which.max(table(df$sex)))
df$sex <- replace_na(df$sex, majority_sex)

median_capGain <- median(df$capital.gain, na.rm = TRUE)
df$capital.gain <- replace_na(df$capital.gain, median_capGain)

majority_natCountry <- names(which.max(table(df$native.country)))
df$native.country <- replace_na(df$native.country, majority_natCountry)

```




