
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 9: Visualization - Revealing a graph"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment9.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

**Notice:** *In this assignment, all the plot should have title, caption, and axis labels. *

1. Use the dataset by of covid 19 by WHO at https://covid19.who.int/WHO-COVID-19-global-data.csv. Find the three countries with the most numbers of deaths by Covid-19. 

Hint: 

-  Use `filter` to select the most current date 

-  Pipe with `arrange(-Cumulative_deaths)` to rank the data by the number of cumulative deaths

```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(lubridate)
library(gganimate)

df <- read_csv("https://covid19.who.int/WHO-COVID-19-global-data.csv")

df %>% 
  filter(Date_reported=="2023-10-04") %>% 
  arrange(-Cumulative_deaths)
#US, Brazil, and India
```

2. Use `transition_reveal` to make a plot revealing the number of deaths in the three countries with the most numbers of deaths

```{r}
df %>% 
  filter(Country=="United States of America"|Country=="Brazil"|Country=="India") %>% 
  ggplot(aes(x=Date_reported, y=Cumulative_deaths, color = Country))+
  geom_line()+
  transition_reveal(Cumulative_deaths)
  
```

3. Create the new variable (column) `death_per_cases` recording the number of deaths per cases (Hint: divide cumulative deaths by cumulative cases).  What are the three countries with the highest deaths per cases? 

```{r}
df$death_per_cases <- df$Cumulative_deaths/df$Cumulative_cases

df %>% filter(Date_reported == max(Date_reported)) %>% arrange(-death_per_cases) %>% top_n(3,death_per_cases)
#Yemen, Sudan, Syrian Arab Republic
```

4. Use `transition_reveal` to make a plot revealing the number of deaths per cases of the US, Italy and Mexico. 

```{r}
df %>% 
  filter(Country=="United States of America"|Country=="Italy"|Country=="Mexico") %>% 
  ggplot(aes(x=Date_reported, y=death_per_cases, color = Country))+
  geom_line()+
  transition_reveal(Cumulative_deaths)
```

5. Import the following data https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations.csv

```{r}
df2 <- read_csv("https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/vaccinations.csv")
```
                      
Use `transition_reveal` to plot the total vaccinations per hundred by level of income. Hint: the levels of income are identified in the `location` variable. Put a short comment on the caption of the plot. 

```{r}
df2 %>% 
  filter(location %in% c("Lower middle income", "Low income", "Upper middle income")) %>% 
  ggplot(aes(y=total_vaccinations_per_hundred,
            x=date,
            color=location))+ 
  geom_line()+
  geom_point(size=1)+
  transition_reveal(date)+
  labs(caption = 'Total vaccinations per hundred by level of income')
```

