
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 12: Predictive Modeling - Part 3"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment12.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


1. Use the `PimaIndiansDiabetes` dataset. Use 15% data for testing. Use cross-validation with of 7 folds to tune random forest `(method='ranger')`.  What are the parameters that produce the greatest accuracy? What is the testing accuracy. 

```{r}
library(mlbench)
library(tidyverse)
library(caret)

data(PimaIndiansDiabetes)
df <- tibble(PimaIndiansDiabetes)

df = drop_na(df)
df <- df %>% rename(target=diabetes)
splitIndex <- createDataPartition(df$target, p = .85, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]

model1 <- train(target~., data=df_train, 
                method = "ranger",
                maxdepth=7)

pred <- predict(model1, df_test)
cm <- confusionMatrix(data = pred, reference = df_test$target)

cm$overall[1]
print(model1)
```

2. Use the `PimaIndiansDiabetes` dataset. Go to https://topepo.github.io/caret/available-models.html and pick a classification model.  Tune the classification model using cross-validation of 7 folds. 

```{r}
library(tidyverse)
library(adabag)
library(caret)
library(mlbench)
library(dplyr)

df <- tibble(PimaIndiansDiabetes)
df = drop_na(df)
df <- df %>% rename(target=diabetes)

splitIndex <- createDataPartition(df$target, p = .85, 
                                  list = FALSE)

df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]

tr_control = trainControl(method = "cv", number = 7)
tuneGrid = expand.grid(mfinal = 10, maxdepth = c(1:10))

model1 <- train(target ~., data = df_train, method = "AdaBag", trControl = tr_control, tuneGrid = tuneGrid)

plot(model1)
```

3. (Model Comparison) Use the `PimaIndiansDiabetes` dataset. Pick two models at [this link](https://topepo.github.io/caret/available-models.html) to compare using 7-fold cross validation method. Evaluate the accuracy of the final model on the test data. 

```{r}
library(tidyverse )
df <- tibble(PimaIndiansDiabetes)
df = drop_na(df)
df <- df %>% rename(target=diabetes)
splitIndex <- createDataPartition(df$target, p = .85, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
model2 <- train(target~., data=df_train, 
                method = "rpart2",
                maxdepth=7)
pred <- predict(model2, df_test)
cm <- confusionMatrix(data = pred, reference = df_test$target)
cm$overall[1]


df <- tibble(PimaIndiansDiabetes)
df = drop_na(df)
df <- df %>% rename(target=diabetes)
splitIndex <- createDataPartition(df$target, p = .85, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]
model3 <- train(target~., data=df_train, 
                method = "glmnet",
                maxdepth=7)
pred <- predict(model3, df_test)
cm <- confusionMatrix(data = pred, reference = df_test$target)
cm$overall[1]
```

