
---
title: "Adult Census - Check Box"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: download.png
    source_code: embed
    social: menu

runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(flexdashboard)
library(tidyverse)
library(plotly)
library(knitr)
library(DT)

df <- read_csv("https://bryantstats.github.io/math421/data/adult_census.csv")

census_education <- unique(df$education)

```

{.sidebar}
=======================================================================

This census data set consists of 15 variables, and is a mix of both numerical and categorical variables. The target variable is the "income", since the data set is used to predict whether or not the observation's salary has greater than or less than $50k, using the variables and demographics from the adult census data. Select input(s) for the plots to see how income results impacts other census results:

```{r}
checkboxGroupInput(inputId = "income_input", 
                   label = h3("Income Level"),
                   choices = unique(df$income), 
                   inline = TRUE,
                   selected = "<=50K")

```

Main Tab 1
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Density Plot

```{r}
renderPlotly({
  plot1 <- df %>% 
    filter(income %in% input$income_input) %>% 
    ggplot(aes(x=hours.per.week, color=sex))+
    geom_density()
  ggplotly(plot1)
})
```

Column {data-width=500}
-----------------------------------------------------------------------

### Bar Plot

```{r}
renderPlotly({
  plot2 <- df %>% 
    filter(income %in% input$income_input) %>% 
    ggplot(aes(y=occupation, fill=sex))+
    geom_bar()
  ggplotly(plot2)
})
```
